### 2014-07-15 Paper1/paper1.tex
Updated paper 1, updating toy extract. Need matlab class

For typical dynamic simulations, in order to determine the trajectory of the system (i.e., the forward dynamics problem), this second-order differential equation is typically solved by numerical integration to determine the solution to the initial value problem in time. This first involves algebraic manipulation to solve for $\ddot{q}$, and then integration to determine the state trajectory. Intent determination takes the novel approach of instead solving for $\ddot{q}_d$:
\begin{equation}
\ddot{q}_d=\hat{M}(q_d)^{-1}\left\{M(q)\ddot{q}+G(q,\dot{q})+E-[\hat{G}(q_d,\dot{q}_d)+\hat{E}+K_p(q_d-q)+K_d(\dot{q}_d-\dot{q})]\right\}
\end{equation}  
$\ddot{q}_d$ can then be integrated to determine the intended state trajectory $q_d(t)$. This relies on many assumptions: The model of plant and controller must be accurate and precise. The initial conditions must be available and accurate. The mass matrix estimate, $\hat{M}$, must be invertible. Externally-applied force must be precisely and accurately measured. If all of these conditions are met, then the system yields an accurate estimate of the intent.

It is important to distinguish our intended trajectory, $q_d$, from another variable often considered, the equilibrium point of the muscle actuators. Importantly, this has been claimed to be the intended movement. To consider this, we also generalize our approach to any system with a moving intention that governs the control law. This introduces two additional layers of complexity by separating the plant (arm) into its process (dynamics) and actuator components (muscles) and considering the actuator's equilibrium, $q_e$ (sometimes represented as $\lambda$). The feedforward component must use and share this actuator and hence use the actuator's equilibrium. Without loss of generality, we represent the process $P$ and actuator $A$ as linear (or linearizable) operations in some space, $x$:
\begin{equation} \label{eq:generalPlant}
\underbrace{\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+\overbrace{\sum_{m=1}^M A_m(x-x_e)^{(m)}}^\text{Actuator}}_\text{Plant}+E=0
\end{equation}
The internal model of the process ($\hat{P}$ and $\hat{E}$) predicts system actions, external disturbances, and impedance responses in order to determine $x_e$ that $x$ will track a desired path $x_d$.    
\begin{equation}
\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m(x_d-x_e)^{(m)}}^\text{Actuator}=0
\end{equation}
We solve this for $x_e$ and substituting into \eqref{eq:generalPlant} gives:
\begin{equation}
\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+E=\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m (x_d-x)^{(m)}}^\text{Feedback (Actuator)}
\end{equation}

@@

While the derivation of intent determination required many steps, the outcome is a filter whose use is straight-forward. Many filters for converting assumed intent into simulated hand trajectories have been proposed and validated \cite{shadmehr1994adaptive, franklin2003adaptation, burdet2006stability}. Demonstrating the validity and plausibility of mathematically transforming those filters to instead covert measured hand trajectories to intent adds a novel method to the arsenal of analytical methods for exploring human motor control.

@@

This novel determination of intended trajectories from force-disturbed movements allows hypothesis testing that was not previously possible. This approach can take \textbf{any} ``candidate model'' of the human arm and create a filter that estimates the intended trajectory. By using tests such as the comparison with undisturbed straight line reaching employed in this paper, one can evaluate which candidate produces the most plausible intended trajectory, supporting one model over another.  Instead of comparing two generative models to see which better approximates movement, it is now possible to perform element-by-element fitting. Direct access to the intended trajectory allows optimal feedback control models to better understand and fit hypothesized cost functions and their parameters. In addition, mid-movement replanning became falsifiable: we were able to show that intended trajectories from disturbed motions differ from those undisturbed motions and how they differed.

>>>>

For typical dynamic simulations, in order to determine the trajectory of the system (i.e., the forward dynamics problem), this second-order differential equation is solved by numerical integration to determine the solution to the initial value problem in time. This first involves algebraic manipulation to solve for $\ddot{q}$, and then integration to determine the state trajectory. Intent determination takes the novel approach of instead solving for $\ddot{q}_d$:
\begin{equation}
\ddot{q}_d=\hat{M}(q_d)^{-1}\left\{M(q)\ddot{q}+G(q,\dot{q})+E-[\hat{G}(q_d,\dot{q}_d)+\hat{E}+K_p(q_d-q)+K_d(\dot{q}_d-\dot{q})]\right\}
\end{equation}  
$\ddot{q}_d$ can then be integrated to determine the intended state trajectory $q_d(t)$. This relies on many assumptions: The model of plant and controller must be accurate and precise. The initial conditions must be available and accurate. The mass matrix estimate, $\hat{M}$, must be invertible. Externally-applied force must be precisely and accurately measured. If all of these conditions are met, then the system yields an accurate estimate of the intent.

It is important to distinguish our intended trajectory, $q_d$, from another variable often considered, the equilibrium point of the muscle actuators. Importantly, this has been claimed to be the intended movement. To consider this, we also generalize our approach to any system with a moving intention that governs the control law. This introduces two additional layers of complexity by separating the plant (arm) into its process (dynamics) and actuator components (muscles) and considering the actuator's equilibrium, $q_e$ (sometimes represented as $\lambda$). The feedforward component must use and share this actuator and hence use the actuator's equilibrium. Without loss of generality, we represent the process $P$ and actuator $A$ as linear (or linearizable) operations in some space, $x$:
\begin{equation} \label{eq:generalPlant}
\underbrace{\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+\overbrace{\sum_{m=1}^M A_m(x-x_e)^{(m)}}^\text{Actuator}}_\text{Plant}+E=0
\end{equation}
The internal model of the process ($\hat{P}$ and $\hat{E}$) predicts system actions, external disturbances, and impedance responses in order to determine $x_e$ such that $x$ will track a desired path $x_d$.    
\begin{equation}
\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m(x_d-x_e)^{(m)}}^\text{Actuator}=0
\end{equation}
We solve this for $x_e$ and substituting into \eqref{eq:generalPlant} gives:
\begin{equation}
\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+E=\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m (x_d-x)^{(m)}}^\text{Feedback (Actuator)}
\end{equation}

@@

While the derivation of intent determination required many steps, the outcome is a filter whose use is straight-forward. Many filters for converting assumed intent into simulated hand trajectories have been proposed and validated \cite{shadmehr1994adaptive, franklin2003adaptation, burdet2006stability}. Demonstrating the validity and plausibility of mathematically transforming those filters to instead convert measured hand trajectories to intent adds a novel method to the arsenal of analytical methods for exploring human motor control.

@@

This novel determination of intended trajectories from force-disturbed movements allows hypothesis testing that was not previously possible. This approach can take \textbf{any} ``candidate model'' of the human arm and create a filter that estimates the intended trajectory. By using tests such as the comparison with undisturbed straight line reaching employed in this paper, one can evaluate which candidate produces the most plausible intended trajectory, supporting one model over another.  Instead of comparing two generative models to see which better approximates movement, it is now possible to perform element-by-element fitting. Direct access to the intended trajectory allows optimal feedback control models to better understand and fit hypothesized cost functions and their parameters. In addition, mid-movement replanning became falsifiable: we were able to show that intended trajectories from disturbed motions differ from those of undisturbed motions and how they differed.
